---
title: "Top 10 Asian Restaurants in Boston From YELP!"
author: "CHEN HONG"
date: "5/7/2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r,message=F,echo=F,warning=F}
library(tidyverse)
library(httr)
library(ggplot2)
library(stringr)
library("tm")
library("SnowballC")
library("RColorBrewer")
library(wordcloud)
library(leaflet)
```

```{r,message=F,echo=F,warning=F}
#knitr::opts_chunk$set(echo = FALSE)
# R version 3.4.4 (2018-03-15)



yelp_result <- function(keyword, num_of_business){
api_key <- "0cFq1_x0M3Th7jRukCHXdPlxXXdIg0OSP5YCN5sAARZMFEmgYKQdja8A8HpI8xRe51nC6-JCZjeGWUaZh92xrOFGKvKFITn5ENbiNkPkMqw_0wupzQTiQrIhsEvhWnYx"
client_id <- "mkwzEaUHww2bepzeXx2JaqA"
client_secret <- api_key

response <- POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
                        client_id = client_id,
                        client_secret = client_secret))

#token <- content(response)$access_token


# extrat the data from YELP
yelp <- "https://api.yelp.com"
term <- keyword
location <- "Boston, MA"
categories <- NULL
limit <- num_of_business
radius <- 8000
url <- modify_url(yelp, path = c("v3", "businesses", "search"),
                  query = list(term = term, location = location, 
                               limit = limit,
                               radius = radius))
res <- GET(url, add_headers(Authorization = paste("Bearer", api_key)))
return(content(res))
}



yelp_summary_in_dataframe <- function(results) {
rows = length(results$business)
result_df <- data.frame(matrix(nrow = rows, ncol = 7))
colnames(result_df) <- c("name", "price", "rating","review", "c1", "c2", "c3")
for (i in 1:rows) {
  result_df[i, 1] <- results$business[[i]]$name
  result_df[i, 2] <- results$business[[i]]$price
  result_df[i, 3] <- results$business[[i]]$rating
  result_df[i, 4] <- results$business[[i]]$review_count
  cat_column_index <- 5
  for(num in 1:length(results$business[[i]]$categories)) {
    result_df[i, cat_column_index] <- results$business[[i]]$categories[[num]]$title
    cat_column_index <- cat_column_index + 1
  }
}
return(result_df)
}

get_average <- function(df_col){
  return(mean(df_col))
}


category_word_colud <- function(dataframe){
  dataframe$c1 <- paste(dataframe$c1, dataframe$c2, dataframe$c3)
  ##str(dataframe$c1)
  wordcloud(words = dataframe$c1, 
            min.freq=1, 
            random.order = FALSE,
            rot.per=.5,colors=brewer.pal(8, "Dark2"))
}


```

## Top 10 Asian Restaurants in Boston 
This realtime Data is extraced from YELP! with lists information of 50 restaurants of their reviews, ranking , location and price levels. I use the criteria of price, ranking , number of reviews etc and filter out the top 10 asian restaurants in boston. and made a geographical map with location marks tagged with restaurants details. 




## The 50 asian restaurants in boston with a radius 8000 

- Asian Restaurants 
- Price & Rating Statistic Relationship
- Filtered out top 10 and map info 

## Collection of 50 Asian Restaurants with radius 8000 centerd Boston 
- the word cloud with frequency 

```{r,message=F,echo=F,warning=F}
df <- read_csv("df1.csv")
rating_avg <- get_average(df$rating)
review_avg <- get_average(df$review)
is.numeric(df$review_count)
category_word_colud(df)

```

## The Statistic Relation Between Rating and Price

```{r,message=F,echo=F,warning=F}
rating <- df$rating
price <- df$price
pricen<- str_length(price)
is.numeric(pricen)
### the regression between the price and the rating 


model <- lm(pricen~rating)
summary(model)
anova(model)
cor(pricen,rating)

```

## Bar Plot of the Cuisines Types
the above is the barplot of the cuisines categories. we can apparently notice that Asian Fusion 
is the most frequently served, to be more specific, the sushi bars, chinese cuisines, thai 
japeanses and ramen are most ofter served.


```{r,message=F,echo=F,warning=F}
category_df <- df[c("c1", "c2", "c3")]
View(category_df)
as.data.frame(category_df)
df_c1 <- category_df[c("c1")]
colnames(df_c1) <- c("cat")
df_c2 <- category_df[c("c2")]
colnames(df_c2) <- c("cat")
df_c3 <- category_df[c("c3")]
colnames(df_c3) <- c("cat")
category150 <- rbind(df_c1, df_c2, df_c3)
View(category150)


cat_freq_bar_chart <- function(cat_df){
freq_list <- as.data.frame(table(unlist(cat_df)))
colnames(freq_list) <- c("category", "frequency")
data <- data.frame(
  category=freq_list$category,
  frequency=freq_list$frequency
)

data %>%
  mutate(name = fct_reorder(category, frequency)) %>%
  ggplot( aes(x=category, y=frequency)) +
  geom_bar(stat="identity") +
  coord_flip()
}

cat_freq_bar_chart(category150)

```

## top 10 Asian Retaurants in Boston 
After filter by the average rating and price level, here are top 10 consumer-friednly restaurants in Boston 

```{r,message=F,echo=F,warning=F}
top <- df %>% filter(rating > rating_avg) %>% filter(review > review_avg)
top

```